Model

### 2019-11-26 stats/kids_basic_me.Rmd
make age discrete in month

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  filter(trial != "train1",
           trial != "train2")%>%
  mutate(item = familiar,
         age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiar, -rt)

@@

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% d$familiar )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         familiar = Word)%>%
  select(familiar,mean_aoa)
```

@@

```{r}
d_model <- d %>%
    filter(trial != "train1",
         trial != "train2")%>%
  mutate(age_num = age_num - mean(age_num))

model <- brm(correct ~ age_num + (1|subid) + (age_num | familiar),
                    data = d_model, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

ranef_plot <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="age_num")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = d$age_num - mean(d$age_num))%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 
         age = age+mean(d$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = familiar))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Mutual Exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

@@

cor_plot <- as_tibble(ranef$familiar, rownames = "familiar") %>%
  left_join(aoa_ratings)

ggplot(cor_plot, aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_point()+
  geom_smooth(method = "lm")+
  xlab("Age of acquisition rating")+
  ylab("ME effect (model intercept)")+
  stat_cor(method = "pearson", label.x = 8, label.y = .99)+
  coord_fixed(ratio = 2)+
  theme_few()

@@

>>>>

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
          age_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_month = round(age_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  filter(trial != "train1",
           trial != "train2")%>%
  mutate(item = familiar,
         age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiar, -rt)

@@

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% d$item )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         item = Word)%>%
  select(item,mean_aoa)
```

@@

model <- brm(correct ~ age + (1|subid) + (age | item),
                    data = d, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          cores = 4, 
          chains = 4,
          save_all_pars = TRUE,
          iter = 2000)

@@

ranef_plot <- as_tibble(ranef$item, rownames = "item")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="age")%>%pull(Estimate))%>%
  group_by(item) %>%
  expand(Estimate.Intercept,Estimate.age,grand_intercept,grand_slope, age = d$age)%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age+grand_slope)*age), 
         age = age+min(d$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Mutual Exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

@@

cor_plot <- as_tibble(ranef$item, rownames = "item") %>%
  left_join(aoa_ratings)

ggplot(cor_plot, aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_point()+
  geom_smooth(method = "lm")+
  xlab("Rated age of acquisition")+
  ylab("ME effect (model intercept)")+
  stat_cor(method = "pearson", label.x = 5, label.y = .99)+
  coord_fixed(ratio = 3)+
  theme_few()

@@

```{r}
ggsave("../graphs/talk_me_rating_cor.pdf", width = 4, height = 4, scale = 1)
```

### 2019-11-26 stats/kids_combination.Rmd
make age discrete in month

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

>>>>

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_month = round(age_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
    mutate(age = age_num - min(age_num))%>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)

### 2019-11-26 stats/kids_novelty.Rmd
make age discrete in month

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  mutate(age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -rt)
# 
# 
# ## import mcc data
# 
# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
# 
# raw_data_mcc <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,51,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
# }
# 
# d_raw_mcc <-raw_data_mcc %>%
#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
#          test_date = as.Date(test_date))
# 
# 
# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# 
# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          leftObject = leftFruit,
#          rightObject = rightFruit,
#          pick = str_sub(pick,72,str_length(pick)-4),
#          agent = ifelse(speakerChange == "false", agent,altAgent),
#          experiment = "dis_novelty_mcc")%>%
#   filter(speakerChange == "false", trial != "train")%>%
#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
# 
# 
# # join datasets
# 
# d <- bind_rows(d_spin, d_mcc)
# 
write_csv(d_spin, "../data/novelty.csv")

>>>>

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_month = round(age_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  mutate(age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -rt)
# 
# 
# ## import mcc data
# 
# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
# 
# raw_data_mcc <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,51,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
# }
# 
# d_raw_mcc <-raw_data_mcc %>%
#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
#          test_date = as.Date(test_date))
# 
# 
# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# 
# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          leftObject = leftFruit,
#          rightObject = rightFruit,
#          pick = str_sub(pick,72,str_length(pick)-4),
#          agent = ifelse(speakerChange == "false", agent,altAgent),
#          experiment = "dis_novelty_mcc")%>%
#   filter(speakerChange == "false", trial != "train")%>%
#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
# 
# 
# # join datasets
# 
# d <- bind_rows(d_spin, d_mcc)
# 
write_csv(d_spin, "../data/novelty.csv")

### 2019-11-26 stats/model.Rmd
fix model bug
make age discrete in month

Infer({model,
      samples: 1,
      burn: 1,
      verbose: T,
      lag: 1,
      verboseLag: 1000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

model_comp <- log_like_2%>%
  spread(model,log_like)%>%
  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
         prag_vs_flat_prior = pragmatics - flat_prior,
         prag_vs_prior_only = pragmatics - prior_only)%>%
  group_by(noise)%>%
  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
            prag_vs_prior_only = logSumExp(prag_vs_prior_only))

@@

```{r}
ggplot(log_like_model, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  facet_grid(~parameter)+
  ylim(-1750,-1150)+
  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
    theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())
```

```{r}
ggsave("../graphs/like.png", width = 6, height = 2.5, scale = 1.5)
```

@@

@@

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)

@@

```{r}
data_comb <- read_csv("../data/combination.csv") %>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
         source = "Data")

p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~alignment)+
  ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()+
  scale_fill_viridis_d()
```

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

p_data_model
```

```{r}
ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
```

@@

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

```{r}
#ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
```

@@

# model predictions
prag_model_noise_predictions <- prag_model_noise %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
  mutate(model = "pragmatic_noise")%>%
  group_by(model,age,item, alignment) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         source = "Model")

@@

>>>>

Infer({model,
      samples: 10,
      burn: 10,
      verbose: T,
      lag: 1,
      verboseLag: 1000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

model_comp <- log_like_2%>%
  spread(model,log_like)%>%
  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
         prag_vs_flat_prior = pragmatics - flat_prior,
         prag_vs_prior_only = pragmatics - prior_only)%>%
  group_by(noise)%>%
  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
  gather(model,logP,-noise)

log_like_model_2_free <- log_like_model_2%>%
  filter(noise == "parameter_free")

@@

```{r}
ggplot(log_like_model_2_free, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  #facet_grid(~parameter)+
  #ylim(-1750,-1150)+
  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
    theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())
```

```{r}
ggsave("../graphs/like_talk_free.png", width = 4, height = 2.5, scale = 1.5)
```

@@

#### summaries
item_params_summary <- item_params %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

```{r}
model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")

item_params<- model %>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)

global_params <- model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "parameters")%>%
    separate(value, into = c("int", "slope"),sep = ", ")%>%
    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
    gather(parameter, value, int, slope)

global_params_summary <- global_params %>%
  group_by(token, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))
```

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
) %>%
saveRDS("../saves/prag_model.rds")

comb_model_pred <- readRDS("../saves/prag_model.rds")

@@

```{r}
data_comb <- read_csv("../data/combination.csv") %>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa), 
         source = "Data")

p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "glm", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~alignment)+
  ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()+
  scale_fill_viridis_d()
```

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  #geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

p1 <- data_comb%>%
  group_by(source, alignment, item ,subage)%>%
  multi_boot_standard(col = "correct")

ggplot(p1, aes(x = subage+0.5, y = mean))+
  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, col = source))+
  facet_grid(alignment ~item)+
  #geom_line(aes(group=alignment,col = source))+
  #geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = source),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
  #geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = source), size = 1, alpha = 1)+
  #geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = source), alpha = .5) +
  theme_few()+
  labs(x ="Age", y = "Mutual Exclusivity effect")+
  scale_color_manual(name = "",
                     values = c("#117733", "#117733", "#CC6677"))+
  scale_fill_manual(values = c("#CC6677"))+
  guides(fill = F)+
  theme(legend.position = "bottom")

```{r}
ggsave("../graphs/data_model_talk_00.pdf", width = 12, height = 3.5, scale = 1.2)
```

@@

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Familiar object")
```

```{r}
ggsave("../graphs/talk_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
```

@@

# model predictions
prag_model_noise_predictions <- prag_model_noise %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
  mutate(model = "pragmatic_noise")%>%
  group_by(model,age,item, alignment) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         source = "noisy Model")

@@

### Correlate model predictions and data

binned_noise_model <- prag_model_noise_predictions %>%
  mutate(subage = cut(age, 
                      breaks = c(-0.1,1,2,3),
                      labels = c(2,3,4)))%>%
  group_by(subage, alignment, item)%>%
  summarise(model_mean = estimate_mode(mean),
            model_ci_lower = hdi_lower(mean),
            model_ci_upper = hdi_upper(mean))

cor_plot <- left_join(
  binnned_data,
  binned_noise_model)

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Familiar object")
```

```{r}
ggsave("../graphs/talk_noise_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
```
